### 2017-03-16 CO750-ApproximationAlgorithmsTopics/assignments/assignment_02.tex
Proofreading

Now we intend to show that the hypothesis of the previous lemma holds. Consider some iteration $i$ of $\cA$, and let $A$ be the of edges chosen so far at the end of $i$. Let $B = F \cap A$. Construct a graph $H$ by taking the graph $(V,F)$ and contracting the connected components of $(V,B)$ to vertices. Then $E(H) = F\backslash B$. Let $S_v$ denote the set of vertices in $G$ corresponding to vertex $v \in V(H)$. It is not hard to see that $H$ is a forest. Indeed if $H$ has a cycle $C$ then, since for all $v \in V(C)$, $S_v$ is a connected component in $G$, we can find a cycle $C'$ in $G$ by expanding each $v \in V(C)$ and joining its vertices which lie on $C$ by a path in $S_v$. But $F$ is a forest since it is necessary that any edge $e$ be a bridge to survive the reverse deletion step as $f$ is a $01$-function (observe that for all $S$ $|\delta(S) \backslash \{e\}| \geq 1 \geq f(S)$ if $e$ is not a bridge).

@@

We begin by working towards a compact formulation for $(IP)$ on $G$. Since $G$ is a cycle we may label the vertices of $G$ as $V(G) = \{v_1,\dots, v_n\}$ such that $v_iv_j \in E(G)$ if and only if $$j \equiv i\pm1\mod n$$. For $v_i, v_j \in V(G)$ we define the path from $v_i$ to $v_j$ as 

@@

Let $e \in E$. If $\bar{x}(e) < 0.5$ then we have immediately $x(e) \leq \bar{x}(e)$ and so trivially we have $x(e) \leq 2\bar{x}(e)$. It remains to consider the pertinent case when $\bar{x}(e) \geq 0.5$. Therein we have

@@

$$\sum_{e\in E}c(e) x(e) \leq \sum_{e \in E}c(e)2\bar{x}(e) = 2\sum_{e\in E}\bar{x}(e) \leq 2\cdot OPT,$$

@@

If there exists an optimal solution $x^*$ for $(\overline{IP})$ and $e \in E$ such that $x^*(e) = 0$ then $x^*(e) = x^{e}$ by lemma \ref{lemma:0edge} and $e \in E'$. Thus in step $5$ $\cA'$ returns a solution of cost at most that of $x^{e} = x^*$ which is therefore optimal. Trivially such a solution is of cost at most $\frac{4}{3}$ that of optimal.

@@

It remains to consider the case where no optimal solution $x^*$ for $(\overline{IP})$ has $e\in E$ such that $x^*(e) = 0$. Since $x^*$ is integral and no component is zero optimal solutions for $(\overline{IP})$ satisfy the constraint $x\geq 1$. Therefore $(\tilde{LP})$ is a relaxation of $(\overline{IP})$.

@@

Now it suffices to show that the returned solution $x$ has cost at most $\frac{4}{3}$ that of $\bar{x}$. Let $e \in E$. If $\bar{x}(e) < 0.5$ then we have immediately $x(e) \leq \bar{x}(e)$ and so trivially we have $x(e) \leq \frac{4}{3}\bar{x}(e)$. It remains to consider the pertinent case when $\bar{x}(e) \geq 0.5$. Therein we have

@@

Thus $x(e) \leq \frac{4}{3}\bar{x}(e)$ as desired. 

@@

which in turn, since $e$ corresponds to a tight constraint satisfies

@@

It remains to demonstrate the approximation factor. We will bound the increase in $H$ versus the decrease in the fractional solution at each iteration of step $2$. Let $\Delta_i H$ denote the change in $|H|$ from the beginning of iteration $i$ to the end of iteration $i$.. Exactly one set is added to $H$ in each iteration so $\Delta_i H = 1$ for all $i$. Let $x^i$ be the fractional solution to $(LP)$ found at the beginning of iteration $i$. Let $\Delta_i x = \sum_{S \in \cS}x^{i}_S - \sum_{e \in \cS}x^{i+1}_S$, where we take $x^{n+1} = 0$ if step $2$ terminates in $n$ iterations, and take $x^{i}_S = 0$ if $S \not\in \cS'$ during iteration $i$.

@@

Academic Honesty Disclaimer: In this problem I rely heavily on her paper Dr. Sanita gave us on Learn: Steiner Tree Approximation via Iterative Randomized Rounding.

@@

\item Return Witness Tree $W= \{\{u,v\} in {R\choose 2} : |P_uv \cap \tilde{B}| = 1\}$.

@@

By lemma \ref{lemma:four} and the preceding discussion, this procedure covers all possible forms the components $Z_i$ can take. Further one can verify that $W$ is a terminal spanning tree. 

@@

For any $e \in E(S^*)$ we define $W(e) = \{ uv \in E(W): e \in P_{uv}\}$. When the edges of $W(e)$ are $\textit{marked}$ (see paper) the edge $e$ is deleted. We have the following lemma from the paper/class (rephrased in terms of $W(e)$ for simplicity):

>>>>

Now we intend to show that the hypothesis of the previous lemma holds. Consider some iteration $i$ step $2$ of $\cA$, and let $A$ be the of edges chosen so far at the end of $i$. Let $B = F \cap A$. Construct a graph $H$ by taking the graph $(V,F)$ and contracting the connected components of $(V,B)$ to vertices. Then $E(H) = F\backslash B$. Let $S_v$ denote the set of vertices in $G$ corresponding to vertex $v \in V(H)$. It is not hard to see that $H$ is a forest. Indeed if $H$ has a cycle $C$ then, since for all $v \in V(C)$, $S_v$ is a connected component in $G$, we can find a cycle $C'$ in $G$ by expanding each $v \in V(C)$ and joining its vertices which lie on $C$ by a path in $S_v$. But $F$ is a forest since it is necessary that any edge $e$ be a bridge to survive the reverse deletion step as $f$ is a $01$-function (observe that for all $S$ $|\delta(S) \backslash \{e\}| \geq 1 \geq f(S)$ if $e$ is not a bridge).

@@

We begin by working towards a compact formulation for $(IP)$ on $G$. Since $G$ is a cycle we may label the vertices of $G$ as $V(G) = \{v_1,\dots, v_n\}$ such that $v_iv_j \in E(G)$ if and only if $$j \equiv i\pm1\mod n.$$ For $v_i, v_j \in V(G)$ we define the path from $v_i$ to $v_j$ as 

@@

Let $e \in E$. If $\bar{x}_F(e) < 0.5$ then we have immediately $x(e) \leq \bar{x}(e)$ and so trivially we have $x(e) \leq 2\bar{x}(e)$. It remains to consider the pertinent case when $\bar{x}_F(e) \geq 0.5$. Therein we have

@@

$$\sum_{e\in E}c(e) x(e) \leq \sum_{e \in E}c(e)2\bar{x}(e) = 2\sum_{e\in E}c(e)\bar{x}(e) \leq 2\cdot OPT,$$

@@

If there exists an optimal solution $x^*$ for $(\overline{IP})$ and $e \in E$ such that $x^*(e) = 0$ then $x^* = x^{e}$ by lemma \ref{lemma:0edge} and $e \in E'$. Thus in step $5$, $\cA'$ returns a solution of cost at most that of $x^{e} = x^*$ which is therefore optimal. Trivially such a solution is of cost at most $\frac{4}{3}$ that of optimal.

@@

It remains to consider the case where no optimal solution $x^*$ for $(\overline{IP})$ has $e\in E$ such that $x^*(e) = 0$. Since $x^*$ is integral and no component is zero optimal solutions for $(\overline{IP})$ satisfy the constraint $x\geq 1$. Therefore $(\tilde{LP})$ is a relaxation of $(\overline{IP})$ in this case.

@@

Now it suffices to show that the returned solution $x$ has cost at most $\frac{4}{3}$ that of $\bar{x}$. Let $e \in E$. If $\bar{x}_F(e) < 0.5$ then we have immediately $x(e) \leq \bar{x}(e)$ and so trivially we have $x(e) \leq \frac{4}{3}\bar{x}(e)$. It remains to consider the pertinent case when $\bar{x}_F(e) \geq 0.5$. Therein we have

@@

Thus $x(e) \leq \frac{4}{3}\bar{x}(e)$ as desired. Therefore
$$\sum_{e\in E}c(e) x(e) \leq \sum_{e \in E}c(e)\frac{4}{3}\bar{x}(e) = \frac{4}{3}\sum_{e\in E}c(e)\bar{x}(e)$$
and the approximation factor follows.

@@

which in turn, since $e$ corresponds to a tight constraint, satisfies

@@

It remains to demonstrate the approximation factor. We will bound the increase in $H$ versus the decrease in the fractional solution at each iteration of step $2$. Let $\Delta_i H$ denote the change in $|H|$ from the beginning of iteration $i$ to the end of iteration $i$. Exactly one set is added to $H$ in each iteration so $\Delta_i H = 1$ for all $i$. Let $x^i$ be the fractional solution to $(LP)$ found at the beginning of iteration $i$. Let $\Delta_i x = \sum_{S \in \cS}x^{i}_S - \sum_{e \in \cS}x^{i+1}_S$, where we take $x^{n+1} = 0$ if step $2$ terminates in $n$ iterations, and take $x^{i}_S = 0$ if $S \not\in \cS'$ during iteration $i$.

@@

When I refer to ``the paper" below, I mean Dr. Sanita's paper she gave us on Learn: Steiner Tree Approximation via Iterative Randomized Rounding.

@@

\item Return Witness Tree $W= \{\{u,v\} \in {R\choose 2} : |P_{uv} \cap \tilde{B}| = 1\}$.

@@

By lemma \ref{lemma:four} and the preceding discussion, this procedure covers all possible forms the components $Z_i$ can take. Further it is immediate from our choice of $\tilde{B}$ that $W$ is a terminal spanning tree. A simple inspection of the edges taken in $W$ with respect to the terminals of each $Z_i$ verifies this.

@@

For any $e \in E(S^*)$ we define $W(e) = \{ uv \in E(W): e \in P_{uv}\}$. When the edges of $W(e)$ are $\textit{marked}$ (see the paper) the edge $e$ is deleted. We have the following lemma from the paper/class (rephrased in terms of $W(e)$ for simplicity):
